---
title: "Adjusted BGG Ratings"
output: 
  html_document:
    toc: TRUE #adds a Table of Contents
    number_sections: TRUE #number your headings/sections
    toc_float: TRUE #let your ToC follow you as you scroll
    keep_md: no
    fig.caption: yes
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = F,
                      error=F,
                      dev="png",
                      fig.width = 10,
                      fig.height = 6)

options(knitr.duplicate.label = "allow")

options(scipen=999)

# load packages to be used
source(here::here("scripts/load_packages.R"))

# load custom functions to be used
source(here::here("functions/theme_phil.R"))
source(here::here("functions/tidy_name_func.R"))
source(here::here("scripts/load_packages.R"))
source(here::here("functions/average_col_func.R"))
source(here::here("functions/bayesaverage_col_func.R"))
source(here::here("functions/usersrated_col_func.R"))
source(here::here("functions/complexity_col_func.R"))
source(here::here("functions/get_bgg_data_from_github.R"))

```

```{r flextable settings, echo=F, warning=F, message=F, results='hide'}

#library(webshot2)
library(flextable)
set_flextable_defaults(theme_fun = theme_alafoli,
                       font.color = "grey10",
  padding.bottom = 6, 
  padding.top = 6,
  padding.left = 6,
  padding.right = 6,
  background.color = "white")

```

```{r load most recent data}

# list all files
ratings_files = list.files(here::here("adjusted_ratings")) %>%
        as_tibble() %>%
        mutate(file = value) %>%
        separate(value, into = c("date", "type"), sep="\\.") %>%
        mutate(date = as.Date(date))

# get most recent
most_recent_file = ratings_files %>% filter(date == max(date)) %>% pull(file)

# load in
active_ratings = fread(here::here("adjusted_ratings",
                                            paste(most_recent_file)))

```

```{r connect to big query and query tables we need, warning=F, message=F, results='hide'}

library(bigrquery)

# get project credentials
PROJECT_ID <- "gcp-analytics-326219"
BUCKET_NAME <- "test-bucket"

# authorize
bq_auth(email = "phil.henrickson@aebs.com")

# establish connection
bigquerycon<-dbConnect(
        bigrquery::bigquery(),
        project = PROJECT_ID,
        dataset = "bgg"
)

# query table of game info to most recent load
active_games<-DBI::dbGetQuery(bigquerycon, 
                              'SELECT * FROM bgg.api_game_info
                              where timestamp = (SELECT MAX(timestamp) as most_recent FROM bgg.api_game_info)') %>%
        select(-starts_with("rank")) %>%
        mutate(numweights = as.numeric(numweights)) %>%
        mutate_at(c("averageweight",
                    "playingtime",
                    "minplaytime",
                    "maxplaytime",
                    "yearpublished"),
                  ~ case_when(. == 0 ~ NA_real_,
                              TRUE ~ .))

# get games from today
bgg_today = get_bgg_data_from_github(Sys.Date())

```

Last Updated: `r active_ratings$date[1]`

# Complexity Adjusted Ratings

These rankings are designed to adjust for the strong correlation between complexity and a game's average rating on BGG. Sorting by the 'Adjusted' rating will help highlight games that are **highly popular** on BGG while also being **easy to learn**.

```{r data table with complexity adjusted ratings, warning=F, message=F}

active_ratings %>%
        left_join(., bgg_today %>%
                          select(-date),
                  by = c("game_id")) %>%
        left_join(., active_games %>%
                          select(game_id, averageweight),
                  by = c("game_id")) %>%
        rename(Complexity = averageweight) %>%
        mutate_at(vars(game_release_year,
                    game_id),
                  as.character) %>%
        rename(bayesaverage = bayes_average) %>%
        rename(Published = game_release_year,
               ID = game_id,
               Name = name,
               UsersRated = users_rated,
               Average = bgg_average,
               Geek = bayesaverage,
               Adjusted = adj_bayesaverage) %>%
        select(Published, ID, Name, UsersRated, Complexity, Average, Geek, Adjusted) %>%
        mutate_if(is.numeric, round, 2) %>%
        arrange(desc(Adjusted)) %>%
        DT::datatable()

```

# "Hotness" Adjusted Rankings

These rankings amend the existing formula for the geek rating by altering the number of baseline votes. This mitigates the tendency for the geek ratings to highlight recently released games.

The current geek rating, roughly, amounts to adding **1000** ratings of 5.5 to any game. In order for a game to improve its geek rating, it needs to accumulate ratings that are higher than 5.5.

This table displays the rankings of games if we toggle the number of baseline votes from the current setting of **1000** through **100,000**.

```{r display hotness, warning=F, message=F}

active_ratings %>%
        left_join(., bgg_today %>%
                          select(-date),
                  by = c("game_id")) %>%
        mutate_at(vars(game_release_year,
                    game_id),
                  as.character) %>%
        rename(bayesaverage = bayes_average) %>%
        arrange(desc(bayesaverage)) %>%
        rename(Published = game_release_year,
               ID = game_id,
               Name = name,
               UsersRated = users_rated,
               Average = bgg_average,
               Avg_Rank = avg_vote_rank,
               `1k Rank` = votes_1000,
               `5k Rank` = votes_5000,
               `10k Rank` = votes_10000,
               `25k Rank` = votes_25000,
               `100k Rank` = votes_100000) %>%
        select(Published,
               ID,
               Name,
               UsersRated,
               Average,
               Avg_Rank,
               `1k Rank`,
               `5k Rank`,
               `10k Rank`,
               `25k Rank`,
               `100k Rank`) %>%
        mutate_if(is.numeric, round, 2) %>%
        DT::datatable()

```

