---
title: "Predicting Upcoming Boardgames"
output: 
  html_document:
    toc: TRUE #adds a Table of Contents
    number_sections: TRUE #number your headings/sections
    toc_float: TRUE #let your ToC follow you as you scroll
    keep_md: no
    fig.caption: yes
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = F,
                      error=F,
                      dev="png",
                      fig.width = 10,
                      fig.height = 6)

options(knitr.duplicate.label = "allow")

options(scipen=999)

# load packages to be used
source(here::here("scripts/load_packages.R"))

# additional libraries
# parallel
library(doParallel)
library(parallelly)

# for stan
library(brms)
library(broom.mixed)

# load custom functions to be used
source(here::here("functions/theme_phil.R"))
source(here::here("functions/tidy_name_func.R"))
source(here::here("functions/pivot_and_dummy_types.R"))
source(here::here("scripts/load_packages.R"))
source(here::here("functions/get_bgg_data_from_github.R"))
source(here::here("functions/get_bgg_data_from_api.R"))
source(here::here("functions/convert_bgg_api_data_to_tables.R"))


source(here::here("functions/predict_bgg_outcomes.R"))
source(here::here("functions/average_col_func.R"))
source(here::here("functions/bayesaverage_col_func.R"))
source(here::here("functions/usersrated_col_func.R"))
source(here::here("functions/complexity_col_func.R"))


```

```{r flextable settings, echo=F, warning=F, message=F, results='hide'}

#library(webshot2)
library(flextable)
set_flextable_defaults(theme_fun = theme_alafoli,
                       font.color = "grey10",
  padding.bottom = 6, 
  padding.top = 6,
  padding.left = 6,
  padding.right = 6,
  background.color = "white")

```


```{r connect to big query and query tables we need, warning=F, message=F, results='hide'}

library(bigrquery)

# get project credentials
PROJECT_ID <- "gcp-analytics-326219"
BUCKET_NAME <- "test-bucket"

# authorize
bq_auth(email = "phil.henrickson@aebs.com")

# establish connection
bigquerycon<-dbConnect(
        bigrquery::bigquery(),
        project = PROJECT_ID,
        dataset = "bgg"
)

# query table of game info to most recent load
active_games<-DBI::dbGetQuery(bigquerycon, 
                              'SELECT * FROM bgg.api_game_info
                              where timestamp = (SELECT MAX(timestamp) as most_recent FROM bgg.api_game_info)') %>%
        select(-starts_with("rank")) %>%
        mutate(numweights = as.numeric(numweights)) %>%
        mutate_at(c("averageweight",
                    "playingtime",
                    "minplaytime",
                    "maxplaytime",
                    "yearpublished"),
                  ~ case_when(. == 0 ~ NA_real_,
                              TRUE ~ .))

# ugh, made a mistake in the schema..

# long table with game type variables
game_types= DBI::dbGetQuery(bigquerycon, 
                              'SELECT * FROM bgg.api_game_categories')


```

```{r functions and workflows}

# get functions
source(here::here("functions/tidy_name_func.R"))
source(here::here("functions/get_bgg_data_from_github.R"))

# load recipe
bgg_outcomes_recipe = readr::read_rds(here::here("models", "active", "base_recipe.Rdata"))

# load workflow
bgg_outcomes_final_workflows = readr::read_rds(here::here("models", "active", "bgg_outcomes_final_workflows.Rds"))

```

```{r assemble data}

# bgg_today 
bgg_today = get_bgg_data_from_github(Sys.Date())

# laod in categorical feature selection we've made use of previously
categorical_features_selected = readr::read_rds(here::here("data",
                                                            "categorical_features_selected.Rdata"))

# now join
games_model = active_games %>%
        left_join(.,
                  game_types %>%
        left_join(., categorical_features_selected %>%
                          select(type, id, value, tidied, selected),
                  by = c("type", "id", "value")) %>%
        filter(selected == 'yes') %>%
        select(game_id, type, value) %>%
        mutate(type_abbrev = substr(type, 1, 3)) %>%
        mutate(value = tolower(gsub("[[:space:]]", "_", gsub("\\s+", " ", gsub("[[:punct:]]","", value))))) %>%
        mutate(type = paste(type, value, sep="_")) %>%
        mutate(has_type = 1) %>%
        select(-value) %>%
        pivot_wider(names_from = c("type"),
                            values_from = c("has_type"),
                            id_cols = c("game_id"),
                            names_sep = "_",
                            values_fn = min,
                            values_fill = 0),
                  by = "game_id") %>%
        rename(numowned = owned)

# discard what you dont need, said aaron downey!
rm(game_types)

# get most recent date
most_recent_date = as.Date(games_model$timestamp[1])

my_caption = list(labs(caption = paste(paste("Data from boardgamegeek.com as of", max(as.Date(active_games$timestamp))),
                        paste("Data and analysis at phenrickson.github.io/data-analysis-paralysis/boardgames.html"), sep="\n")))

```


```{r games to predict}

# get list of games to predict
games_upcoming = games_model %>%
        filter(yearpublished >= 2021) %>%
        rename(owned = numowned) %>%
        mutate(dataset = 'upcoming') %>%
        mutate(log_usersrated = log1p(usersrated)) %>%
        filter(!is.na(yearpublished)) %>%
        filter(usersrated > 1) 
  #      filter(bayesaverage > 0)

games_template = bgg_outcomes_recipe$template

```


```{r now get pieces we need for prediction, warning=F, message=F}

# game_info with estimated averageweight
upcoming_estimated_averageweight = bgg_outcomes_final_workflows %>%
        as_tibble() %>%
        filter(outcome == 'averageweight') %>%
        filter(grepl("xgbTree", wflow_id)) %>%
        mutate(preds = map(.workflow,
                           ~ .x %>%
                                   predict(new_data = games_upcoming) %>%
                                   bind_cols(., games_upcoming %>%
                                                     select(game_id)))) %>%
        select(preds) %>%
        unnest(preds)

# put in estimated averageweight
games_upcoming_estimated = upcoming_estimated_averageweight %>%
        rename(averageweight = .pred) %>%
        left_join(., games_upcoming %>%
                          select(-averageweight),
                  by = "game_id")

# predicting the upcoming set
preds_upcoming = bgg_outcomes_final_workflows %>%
        mutate(preds = map(.workflow,
                           ~ .x %>%
                                   predict(new_data = games_upcoming_estimated) %>%
                                   bind_cols(., games_upcoming_estimated %>%
                                                     select(game_id, name, yearpublished))))
# and now predict
preds_upcoming_tidied = preds_upcoming %>%
        select(outcome, wflow_id, preds) %>%
        unnest() %>%
        mutate(wflow_id = gsub("full_", "", gsub("all_", "", gsub("normalize_", "", wflow_id)))) %>%
        mutate(.pred = case_when(outcome == 'usersrated' ~ plyr::round_any(exp(.pred), 100, ceiling),
                                 TRUE ~ .pred)) %>%
        pivot_wider(names_from = c("outcome", "wflow_id"),
                    values_from = ".pred") %>%
        mutate(bayesaverage_indirect_xgbTree = (
                ((1800*5.5) + (usersrated_xgbTree*average_xgbTree)) /
                        (1800 + usersrated_xgbTree))
               ) %>%
        mutate(bayesaverage_indirect_stan = (
                ((1800*5.5) + (usersrated_stan*average_stan)) /
                        (1800 + usersrated_stan))
               ) %>%
        mutate_if(is.numeric, round, 2) %>%
        arrange(desc(bayesaverage_indirect_xgbTree))

# save this to a location
readr::write_rds(preds_upcoming_tidied,
                 file = here::here("predictions", paste("bgg_outcomes_", Sys.Date(), ".Rdata", sep="")))

```

# Background

What upcoming games on boardgamegeek are expected to be popular? 

I trained a variety of models on historical data from BGG in order to make predictions for upcoming games. My models look at information about games that are known at the time of release - mechanics, player count, playingtime, designer, artist, and selected publishers - and estimates four outcomes on BGG: average weight (complexity), average rating, number of user ratings, and geek rating. I trained the models on games published through 2020 in order to predict upcoming games, which for now refers to games published from 2021 onwards.

For more details on my methodology, see my write up at:
https://phenrickson.github.io/bgg_reports/predicting_bgg_outcomes.html

```{r make a function for flextables}

make_heat_table_func = function(input_preds_table,
                                sort_by,
                                n) {
        
   #      preds_upcoming_tidied %>%
   #      gather("wflow", "pred",
   #             -game_id, -name, -yearpublished) %>%
   # #     filter(grepl("bayesaverage", wflow)) %>%
   #      spread(wflow, pred) %>%
   #      left_join(., games_upcoming %>%
   #                        select(game_id,
   #                               name,
   #                               bayesaverage),
   #                by = c("game_id", "name")) %>%
   #  #    filter(bayesaverage > 0) %>%
   #      select(game_id, name, yearpublished, contains("xgbTree")) %>%
        input_preds_table %>%
        rename(ID = game_id,
               Name = name,
               Published = yearpublished,
               UserRatings = usersrated_xgbTree,
               Weight = averageweight_xgbTree,
               Average = average_xgbTree,
               GeekRating = bayesaverage_indirect_xgbTree) %>%
        arrange(desc(!!enquo(sort_by))) %>%
        mutate_if(is.numeric, round, 2) %>%
        select(Published, ID, Name, UserRatings, Weight, Average, GeekRating) %>%
   #     arrange(desc(GeekRating)) %>%
        mutate(Rank = row_number()) %>%
        mutate_if(is.numeric, round, 2) %>%
        select(Rank, everything()) %>%
                mutate(UserRatings = as.integer(UserRatings)) %>%
        mutate(Link = paste("https://boardgamegeek.com/boardgame/", ID, sep="")) %>%
        mutate(Report = paste("https://phenrickson.github.io/game_report_cards/", ID, ".html", sep="")) %>%
        mutate_at(c("ID",
                       "Published"),
                  ~ as.character(.)) %>%
        head(n) %>%
        flextable(col_keys = c("Rank", "Published", "ID", "Name", "UserRatings", "Weight", "Average", "GeekRating")) %>%
        bg(j = "GeekRating",
           bg = bayesaverage_col_func) %>%
        bg(j="Average",
          bg = average_col_func) %>%
        bg(j = "Weight",
           bg = complexity_col_func) %>%     
        bg(j = "UserRatings",
           bg = usersrated_col_func) %>%   
        bold(j = c("UserRatings",
                   "Average",
                   "GeekRating",
                   "Weight"),
             part = "header") %>%
        flextable::align(j = c("UserRatings",
                               "Average",
                               "GeekRating",
                               "Weight"),
                         align = "center",
                         part = "all") %>%
        add_header_row(values = 
                               c("",
                                 "",
                                 "",
                                 "",
                                 "Estimated",
                                 "Estimated",
                                 "Estimated",
                                 "Estimated")) %>%
        merge_h(part = "header") %>%
        # hline(j = c("UsersRated",
        #                          "Average",
        #                          "GeekRating",
        #                          "Complexity"), 
        #       part = "header") %>%
        autofit() %>%
        compose(j= 3,
                value = as_paragraph(
                        hyperlink_text(x = ID,
                                       url = Link)
                )) %>%
        compose(j= 4,
                value = as_paragraph(
                        hyperlink_text(x = Name,
                                       url = Link)
                )) %>%
        flextable::color(j = c("Name",
                               "ID"),
                         color ="skyblue4") %>%
        compose(j= 5,
                value = as_paragraph(
                        hyperlink_text(x = UserRatings,
                                       url = Report)
                )) %>%
        compose(j= 6,
                value = as_paragraph(
                        hyperlink_text(x = Weight,
                                       url = Report)
                )) %>%
        compose(j= 7,
                value = as_paragraph(
                        hyperlink_text(x = Average,
                                       url = Report)
                )) %>%
        compose(j= 8,
                value = as_paragraph(
                        hyperlink_text(x = GeekRating,
                                       url = Report)
                ))
        
}

```


# Top 100s

In this section, I display the model's top 100 games for the geek rating, average rating, and number of users rated. In each of the tables below, click on the name of the game in order to go directly to the game's boardgamegeek profile, or click on any of the estimated values to go to a report showing how the model arrived at its predictions, along with some other analyses.

## Highest Expected Geek Rating

```{r display preds for geek rating 100}


make_heat_table_func(
        preds_upcoming_tidied %>%
                gather("wflow", "pred",
                       -game_id, -name, -yearpublished) %>%
           #     filter(grepl("bayesaverage", wflow)) %>%
                spread(wflow, pred) %>%
                left_join(., games_upcoming %>%
                                  select(game_id,
                                         name,
                                         bayesaverage),
                          by = c("game_id", "name")) %>%
            #    filter(bayesaverage > 0) %>%
                select(game_id, name, yearpublished, contains("xgbTree")),
        GeekRating,
        100
   )

 
```

## Highest Expected Average Rating 

```{r display preds for average rating 100}

make_heat_table_func(
        preds_upcoming_tidied %>%
                gather("wflow", "pred",
                       -game_id, -name, -yearpublished) %>%
           #     filter(grepl("bayesaverage", wflow)) %>%
                spread(wflow, pred) %>%
                left_join(., games_upcoming %>%
                                  select(game_id,
                                         name,
                                         bayesaverage),
                          by = c("game_id", "name")) %>%
            #    filter(bayesaverage > 0) %>%
                select(game_id, name, yearpublished, contains("xgbTree")),
        Average,
        100
   )

```

## Highest Expected User Ratings

```{r display preds for userrating 100}

make_heat_table_func(
        preds_upcoming_tidied %>%
                gather("wflow", "pred",
                       -game_id, -name, -yearpublished) %>%
           #     filter(grepl("bayesaverage", wflow)) %>%
                spread(wflow, pred) %>%
                left_join(., games_upcoming %>%
                                  select(game_id,
                                         name,
                                         bayesaverage),
                          by = c("game_id", "name")) %>%
            #    filter(bayesaverage > 0) %>%
                select(game_id, name, yearpublished, contains("xgbTree")),
        UserRatings,
        100
   )


```

## Highest Expected Weight

```{r display preds for weight 100}

make_heat_table_func(
        preds_upcoming_tidied %>%
                gather("wflow", "pred",
                       -game_id, -name, -yearpublished) %>%
           #     filter(grepl("bayesaverage", wflow)) %>%
                spread(wflow, pred) %>%
                left_join(., games_upcoming %>%
                                  select(game_id,
                                         name,
                                         bayesaverage),
                          by = c("game_id", "name")) %>%
            #    filter(bayesaverage > 0) %>%
                select(game_id, name, yearpublished, contains("xgbTree")),
        Weight,
        100
   )

```

# Top 100s by Year

In this section, I show the model's top 50 games by expected Geek Rating for individual years.

## 2021

```{r show by year 2021}

make_heat_table_func(

        preds_upcoming_tidied %>%
        gather("wflow", "pred",
               -game_id, -name, -yearpublished) %>%
   #     filter(grepl("bayesaverage", wflow)) %>%
        spread(wflow, pred) %>%
        left_join(., games_upcoming %>%
                          select(game_id,
                                 name,
                                 bayesaverage),
                  by = c("game_id", "name")) %>%
        filter(game_id %in% 
                       (games_upcoming %>%
                                filter(yearpublished == 2021) %>%
                                pull(game_id))) %>%
       # filter(bayesaverage > 0) %>%
        select(game_id, name, yearpublished, contains("xgbTree")),
        GeekRating,
        100
   )

```

## 2022

```{r show by year 2022}

make_heat_table_func(

        preds_upcoming_tidied %>%
        gather("wflow", "pred",
               -game_id, -name, -yearpublished) %>%
   #     filter(grepl("bayesaverage", wflow)) %>%
        spread(wflow, pred) %>%
        left_join(., games_upcoming %>%
                          select(game_id,
                                 name,
                                 bayesaverage),
                  by = c("game_id", "name")) %>%
        filter(game_id %in% 
                       (games_upcoming %>%
                                filter(yearpublished == 2022) %>%
                                pull(game_id))) %>%
       # filter(bayesaverage > 0) %>%
        select(game_id, name, yearpublished, contains("xgbTree")),
        GeekRating,
        100
   )


```

## 2023

```{r show by year 2023}

# boosted trees
make_heat_table_func(

        preds_upcoming_tidied %>%
        gather("wflow", "pred",
               -game_id, -name, -yearpublished) %>%
   #     filter(grepl("bayesaverage", wflow)) %>%
        spread(wflow, pred) %>%
        left_join(., games_upcoming %>%
                          select(game_id,
                                 name,
                                 bayesaverage),
                  by = c("game_id", "name")) %>%
        filter(game_id %in% 
                       (games_upcoming %>%
                                filter(yearpublished == 2023) %>%
                                pull(game_id))) %>%
       # filter(bayesaverage > 0) %>%
        select(game_id, name, yearpublished, contains("xgbTree")),
        GeekRating,
        100
   )

```

# Top 50s by Game Type

In this section, I show games sorted by their expected Geek Rating (a combination of user ratings and average rating), filtering to the top 50 games within specific categories on BGG.

## Fantasy Games

```{r fantasy average top 50}

make_heat_table_func(
        preds_upcoming_tidied %>%
        gather("wflow", "pred",
               -game_id, -name, -yearpublished) %>%
   #     filter(grepl("bayesaverage", wflow)) %>%
        spread(wflow, pred) %>%
        left_join(., games_upcoming %>%
                          select(game_id,
                                 name,
                                 bayesaverage),
                  by = c("game_id", "name")) %>%
        filter(game_id %in% 
                       (games_upcoming %>%
                                filter(category_fantasy==1) %>% 
                                pull(game_id))) %>%
       # filter(bayesaverage > 0) %>%
        select(game_id, name, yearpublished, contains("xgbTree")),
        GeekRating,
        50
   )

```

## Economic Games

```{r Economic average top 50}

make_heat_table_func(
        preds_upcoming_tidied %>%
        gather("wflow", "pred",
               -game_id, -name, -yearpublished) %>%
   #     filter(grepl("bayesaverage", wflow)) %>%
        spread(wflow, pred) %>%
        left_join(., games_upcoming %>%
                          select(game_id,
                                 name,
                                 bayesaverage),
                  by = c("game_id", "name")) %>%
        filter(game_id %in% 
                       (games_upcoming %>%
                                filter(category_economic==1) %>% 
                                pull(game_id))) %>%
       # filter(bayesaverage > 0) %>%
        select(game_id, name, yearpublished, contains("xgbTree")),
        GeekRating,
        50
   )


```


## Wargames

```{r Wargame average top 50}

make_heat_table_func(
        preds_upcoming_tidied %>%
        gather("wflow", "pred",
               -game_id, -name, -yearpublished) %>%
   #     filter(grepl("bayesaverage", wflow)) %>%
        spread(wflow, pred) %>%
        left_join(., games_upcoming %>%
                          select(game_id,
                                 name,
                                 bayesaverage),
                  by = c("game_id", "name")) %>%
        filter(game_id %in% 
                       (games_upcoming %>%
                                filter(category_wargame==1) %>% 
                                pull(game_id))) %>%
       # filter(bayesaverage > 0) %>%
        select(game_id, name, yearpublished, contains("xgbTree")),
        GeekRating,
        50
   )



```

## Science Fiction Games

```{r Science Fiction average top 50}

make_heat_table_func(
        preds_upcoming_tidied %>%
        gather("wflow", "pred",
               -game_id, -name, -yearpublished) %>%
   #     filter(grepl("bayesaverage", wflow)) %>%
        spread(wflow, pred) %>%
        left_join(., games_upcoming %>%
                          select(game_id,
                                 name,
                                 bayesaverage),
                  by = c("game_id", "name")) %>%
        filter(game_id %in% 
                       (games_upcoming %>%
                                filter(category_science_fiction==1) %>% 
                                pull(game_id))) %>%
       # filter(bayesaverage > 0) %>%
        select(game_id, name, yearpublished, contains("xgbTree")),
        GeekRating,
        50
   )

```

## Roll and Writes

```{r roll and writes top 50}

make_heat_table_func(
        preds_upcoming_tidied %>%
        gather("wflow", "pred",
               -game_id, -name, -yearpublished) %>%
   #     filter(grepl("bayesaverage", wflow)) %>%
        spread(wflow, pred) %>%
        left_join(., games_upcoming %>%
                          select(game_id,
                                 name,
                                 bayesaverage),
                  by = c("game_id", "name")) %>%
        filter(game_id %in% 
                       (games_upcoming %>%
                                filter(family_mechanism_rollandwrite==1) %>% 
                                pull(game_id))) %>%
       # filter(bayesaverage > 0) %>%
        select(game_id, name, yearpublished, contains("xgbTree")),
        GeekRating,
        50
   )



```

## Abstracts

```{r abstract average top 50}

make_heat_table_func(
        preds_upcoming_tidied %>%
        gather("wflow", "pred",
               -game_id, -name, -yearpublished) %>%
   #     filter(grepl("bayesaverage", wflow)) %>%
        spread(wflow, pred) %>%
        left_join(., games_upcoming %>%
                          select(game_id,
                                 name,
                                 bayesaverage),
                  by = c("game_id", "name")) %>%
        filter(game_id %in% 
                       (games_upcoming %>%
                                filter(category_abstract_strategy==1) %>% 
                                pull(game_id))) %>%
       # filter(bayesaverage > 0) %>%
        select(game_id, name, yearpublished, contains("xgbTree")),
        GeekRating,
        50
   )


```


## Party Games

```{r Party average top 50}

make_heat_table_func(
        preds_upcoming_tidied %>%
        gather("wflow", "pred",
               -game_id, -name, -yearpublished) %>%
   #     filter(grepl("bayesaverage", wflow)) %>%
        spread(wflow, pred) %>%
        left_join(., games_upcoming %>%
                          select(game_id,
                                 name,
                                 bayesaverage),
                  by = c("game_id", "name")) %>%
        filter(game_id %in% 
                       (games_upcoming %>%
                                filter(category_party_game==1) %>% 
                                pull(game_id))) %>%
       # filter(bayesaverage > 0) %>%
        select(game_id, name, yearpublished, contains("xgbTree")),
        GeekRating,
        50
   )

```

## Card Games

```{r  card average top 50}

make_heat_table_func(
        preds_upcoming_tidied %>%
        gather("wflow", "pred",
               -game_id, -name, -yearpublished) %>%
   #     filter(grepl("bayesaverage", wflow)) %>%
        spread(wflow, pred) %>%
        left_join(., games_upcoming %>%
                          select(game_id,
                                 name,
                                 bayesaverage),
                  by = c("game_id", "name")) %>%
        filter(game_id %in% 
                       (games_upcoming %>%
                                filter(category_card_game==1) %>% 
                                pull(game_id))) %>%
       # filter(bayesaverage > 0) %>%
        select(game_id, name, yearpublished, contains("xgbTree")),
        GeekRating,
        50
   )



```

## Two Player Only Games

```{r two player average top 50}

make_heat_table_func(
        preds_upcoming_tidied %>%
        gather("wflow", "pred",
               -game_id, -name, -yearpublished) %>%
   #     filter(grepl("bayesaverage", wflow)) %>%
        spread(wflow, pred) %>%
        left_join(., games_upcoming %>%
                          select(game_id,
                                 name,
                                 bayesaverage),
                  by = c("game_id", "name")) %>%
        filter(game_id %in% 
                       (games_upcoming %>%
                                filter(family_players_two_player_only_games==1) %>% 
                                pull(game_id))) %>%
       # filter(bayesaverage > 0) %>%
        select(game_id, name, yearpublished, contains("xgbTree")),
        GeekRating,
        50
   )

```


# Interactive Tables

What is the model estimating for upcoming games? The following tables allow users to search for games and examine how the model's predictions compare to the most recent pull of data from BGG.

## User Ratings

```{r interactive table for predictions}

preds_upcoming_tidied %>%
        gather("wflow", "pred",
               -game_id, -name, -yearpublished) %>%
        filter(grepl("usersrated", wflow)) %>%
        spread(wflow, pred) %>%
        left_join(., games_upcoming %>%
                          select(game_id,
                                 name,
                                 bayesaverage,
                                 usersrated),
                  by = c("game_id", "name")) %>%
    #@    filter(bayesaverage > 0) %>%
   #     rename(pred_xgbTree = usersrated_xgbTree) %>%
        rename(pred_stan = usersrated_stan,
               pred_xgbTree = usersrated_xgbTree) %>%
        arrange(desc(pred_xgbTree)) %>%
 #       mutate(estimated = pred_xgbTree) %>%
       # select(game_id, name, yearpublished, usersrated, pred_stan, pred_xgbTree) %>%
        rename(ID = game_id,
               Published = yearpublished,
               Name = name,
               UsersRated = usersrated,
               Predicted = pred_xgbTree) %>%
        select(ID, Published, Name, UsersRated, Predicted) %>%
  #      select(game_id, name, yearpublished, usersrated, pred_stan, pred_xgbTree) %>%
        DT::datatable()

```

## Average Rating

```{r interactive table for predictions average}

preds_upcoming_tidied %>%
        gather("wflow", "pred",
               -game_id, -name, -yearpublished) %>%
        filter(grepl("average", wflow)) %>%
        spread(wflow, pred) %>%
        left_join(., games_upcoming %>%
                          select(game_id,
                                 name,
                                 bayesaverage,
                                 usersrated,
                                 average),
                  by = c("game_id", "name")) %>%
    #    filter(bayesaverage > 0) %>%
   #     rename(pred_xgbTree = average_xgbTree) %>%
        rename(pred_stan = average_stan,
               pred_xgbTree = average_xgbTree) %>%
        arrange(desc(pred_xgbTree)) %>%
 #       mutate(estimated = pred_xgbTree) %>%
       # select(game_id, name, yearpublished, average, pred_stan, pred_xgbTree) %>%
        mutate(Outcome = "Average") %>%
        rename(ID = game_id,
               Published = yearpublished,
               Name = name,
               UsersRated = usersrated,
               Average = average,
               Predicted = pred_xgbTree) %>%
        select(ID, Published, Name, UsersRated, Average, Predicted) %>%
        mutate_if(is.numeric, round, 2) %>%
  #      select(game_id, name, yearpublished, average, pred_stan, pred_xgbTree) %>%
        DT::datatable()

```

## Geek Rating

```{r interactive table for predictions geek rating}

preds_upcoming_tidied %>%
        gather("wflow", "pred",
               -game_id, -name, -yearpublished) %>%
        filter(grepl("bayesaverage", wflow)) %>%
        spread(wflow, pred) %>%
        left_join(., games_upcoming %>%
                          select(game_id,
                                 name,
                                 usersrated,
                                 bayesaverage),
                  by = c("game_id", "name")) %>%
 #       filter(bayesaverage > 0) %>%
        rename(pred_xgbTree = bayesaverage_indirect_xgbTree) %>%
        arrange(desc(pred_xgbTree)) %>%
        mutate_if(is.numeric, round, 2) %>%
        rename(ID = game_id,
               Published = yearpublished,
               Name = name,
               UsersRated = usersrated,
               GeekRating = bayesaverage,
               Predicted = pred_xgbTree) %>%
        select(ID, Published, Name, GeekRating, Predicted) %>%
       # select(game_id, name, yearpublished, usersrated, pred_stan, pred_xgbTree) %>%
        DT::datatable()


```


