---
title: "Predicting Upcoming Games for Reviewers"
output:
  html_document:
    toc: yes
    number_sections: yes
    toc_float: yes
    keep_md: no
    fig.caption: yes
  pdf_document:
    toc: yes
---

```{r load and set packages, echo=F, warning=F, message=F,  results = 'hide', include=F}

knitr::opts_chunk$set(echo = F,
                      error = F,
                      warning=F,
                      dev="png",
                      fig.width = 10,
                      fig.height = 6)

options(knitr.duplicate.label = "allow")

options(scipen=999)

#source
source(here::here("scripts/load_packages.R"))
source(here::here("functions/theme_phil.R"))
library(patchwork)
library(DT)

# set_flextable_defaults(theme_fun = theme_booktabs,
#                        font.color = "black",
#   padding.bottom = 6, 
#   padding.top = 6,
#   padding.left = 6,
#   padding.right = 6,
#   background.color = "white")

library(flextable)
set_flextable_defaults(theme_fun = theme_alafoli,
                       font.color = "grey10",
  padding.bottom = 6, 
  padding.top = 6,
  padding.left = 6,
  padding.right = 6,
  background.color = "white")

```

```{r connect to big query and query tables we need, warning=F, message=F, eval=T, results='hide'}

library(bigrquery)

# get project credentials
PROJECT_ID <- "gcp-analytics-326219"
BUCKET_NAME <- "test-bucket"

# authorize
bq_auth(email = "phil.henrickson@aebs.com")

# establish connection
bigquerycon<-dbConnect(
        bigrquery::bigquery(),
        project = PROJECT_ID,
        dataset = "bgg"
)

# query table of game info to most recent load
active_games<-DBI::dbGetQuery(bigquerycon, 
                              'SELECT * FROM bgg.api_game_info
                              where timestamp = (SELECT MAX(timestamp) as most_recent FROM bgg.api_game_info)') %>%
        select(-starts_with("rank")) %>%
        mutate(numweights = as.numeric(numweights)) %>%
        mutate_at(c("averageweight",
                    "playingtime",
                    "minplaytime",
                    "maxplaytime",
                    "yearpublished"),
                  ~ case_when(. == 0 ~ NA_real_,
                              TRUE ~ .))

# ugh, made a mistake in the schema...

# create caption for plots
my_caption = list(labs(caption = paste(paste("Data from boardgamegeek.com as of", max(as.Date(active_games$timestamp))),
                        paste("Data and analysis at github.com/phenrickson/bgg"), sep="\n")))


# long table with game type variables
game_types= DBI::dbGetQuery(bigquerycon, 
                              'SELECT * FROM bgg.api_game_categories')

```

```{r functions}

# source
source(here::here("functions/tidy_name_func.R"))
source(here::here("functions/get_bgg_data_from_github.R"))

# get user collection
get_user_collection = function(username) {
        
        # load bgg analytics
        library(bggAnalytics)
        
        # load function for grabbing collections
        source(here::here("functions/get_collection.R"))
        
        # load collection
        get_collection(username) %>%
                        as_tibble()
        
}

# function for adding color to flextables
col_func<- function(x) {
  
  breaks<-seq(0, 1, .01)
  
#  breaks = weight_deciles
  colorRamp=colorRampPalette(c("white", "deepskyblue1"))
  col_palette <- colorRamp(length(breaks))
  mycut <- cut(x, 
    breaks = breaks,
    include.lowest = TRUE, 
    right=T,
    label = FALSE)
  col_palette[mycut]
  
}

```

```{r get saved models, warning=F, message=F, results = 'hide', include=F}

#specify bucket and json
Sys.setenv('GCS_AUTH_FILE' = '/Users/Phil/Documents/gcp-analytics-326219-c76fe0dc89d8.json')

# should auto authenticate
library(googleCloudStorageR)

# list of reviewers
reviewers = c("Gyges",
               "ZeeGarcia",
               "Quinns",
               "rahdo",
               "Watch%20It%20Played",
               "J_3MBG",
               "VWValker",
               "aboardgamebarrage",
          #     "markbesada",
           #    "Neilan",
               "Alabaster%20Crippens")

# tidy
reviewers_tidied = gsub("%20", "", reviewers)
               
# get names of their trained models
# suppressMessages({
# user_owned_files = gcs_list_objects(bucket = 'phil_model_storage') %>%
#         as_tibble() %>%
#         filter(grepl("bgg_user_owned", name)) %>%
#         filter(grepl(
#                 paste(
#                         gsub("%20", "", reviewers), 
#                         collapse="|"), name)) %>%
#         pull(name)
# })

user_owned_files = list.files(here::here("user_workflows")) %>%
        as_tibble() %>%
        filter(grepl("bgg_user_owned", value)) %>%
        filter(grepl(
                paste(
                        gsub("%20", "", reviewers),
                        collapse="|"), value)) %>%
        pull(value)

```

```{r get collections from bgg, warning=F, message=F, results = 'hide', include = F}

users = reviewers

# get user collections

user_collections = foreach(i = 1:length(users),
                           .combine = bind_rows,
                           .errorhandling = 'stop') %do% {
                                   get_user_collection(users[i])
                                   }

# tidy user names
user_collections_tidied = user_collections %>%
        mutate(username = gsub("\\%20", "", username)) %>%
        filter(!is.na(rating) | own ==1 | prevowned == 1 | preordered == 1 | want == 1)

# ensure all users are present
nrow(user_collections_tidied %>%
        group_by(username) %>% 
        count()) == length(reviewers)

```

```{r load user workflows}

user_owned_workflows = here::here("user_workflows", user_owned_files) %>%
        map_dfr(readRDS)

# # get saved files
# reviewer_files = list.files(here::here("user_workflows")) %>%
#         grep("temp_reviewer", ., value=T) %>%
#         here::here("user_workflows", .)
# 
# # load
# user_owned_workflows = reviewer_files %>%
#         map_dfr(readRDS)

```


```{r load user owned models from gcs, warning=F, message=F, results = 'hide', include='F'}

# # # pull user workflows from gcs
# suppressMessages({
# 
#         user_owned_workflows = foreach(i = 1:length(user_owned_files),
#         .combine = bind_rows) %do% {
# 
#                 gcs_load(file = user_owned_files[i],
#                          saveToDisk = here::here("user_workflows", user_owned_files[i]),
#                          overwrite = T,
#                          bucket = 'phil_model_storage')
# 
#                 user_workflow = user_owned_workflow
#                 rm(user_owned_workflow)
# 
#                 Sys.sleep(5)
# 
#                 user_workflow
# 
#         }
# 
# })
# 

```


```{r create custom palette}

# define reviewer palette
user_colors = palette.colors(palette = 'Okabe-Ito')
names(user_colors) = reviewers

scale_color_username = scale_color_manual(name = 'username', values = user_colors)
scale_fill_username = scale_fill_manual(name = "username", values = user_colors)

```


```{r load previously stored data and create games model, warning=F, mesage=F, echo=F}

# laod in categorical feature selection we've made use of previously
categorical_features_selected = readr::read_rds(here::here("data",
                                                            "categorical_features_selected.Rdata"))

# select in full game types set
game_types_selected = game_types %>%
        left_join(., categorical_features_selected %>%
                          select(type, id, value, tidied, selected),
                  by = c("type", "id", "value")) %>%
        filter(selected == 'yes')

# pivot and spread these out
game_types_pivoted =game_types_selected %>%
        select(game_id, type, value) %>%
        mutate(type_abbrev = substr(type, 1, 3)) %>%
        mutate(value = tolower(gsub("[[:space:]]", "_", gsub("\\s+", " ", gsub("[[:punct:]]","", value))))) %>%
        mutate(type = paste(type, value, sep="_")) %>%
        mutate(has_type = 1) %>%
        select(-value) %>%
        pivot_wider(names_from = c("type"),
                            values_from = c("has_type"),
                            id_cols = c("game_id"),
                            names_sep = "_",
                            values_fn = min,
                            values_fill = 0)

# now join
games_model = active_games %>%
        left_join(.,
                  game_types_pivoted,
                  by = "game_id") %>%
        rename(numowned = owned) 

rm(game_types_pivoted,
   game_types_selected)

# get most recent date
most_recent_date = as.Date(games_model$timestamp[1])

my_caption = list(labs(caption = paste(paste("Data from boardgamegeek.com as of", max(as.Date(active_games$timestamp))),
                        paste("Data and analysis at https://phenrickson.github.io/data-analysis-paralysis/boardgames.html"), sep="\n")))

# bgg_today 
bgg_today = get_bgg_data_from_github(Sys.Date())

```


```{r join user collections with data, warning=F, message=F}

# join user collection data with bgg games
games_and_collections_data = 
        user_collections_tidied %>%
        mutate(owned = case_when(own == 1 | prevowned == 1 ~ 'yes',
                                         TRUE ~ 'no')) %>%
        mutate(rated = case_when(!is.na(rating) ~ 'yes',
                                         TRUE ~ 'no')) %>%
        mutate(own = case_when(own == 1 ~ 'yes',
                               TRUE ~ 'no')) %>%
        select(username, date, game_id, own, prevowned, owned, rating, rated) %>%
        nest(-username, -date) %>%
        rename(collection = data) %>%
        mutate(games_and_collection = map(collection,
                                          ~ .x %>% right_join(.,
                                                              games_model,
                                                              by = c("game_id")) %>%
                                                  filter(game_id %in% bgg_today$game_id | 
                                                                 game_id %in% .x$game_id))) # trim down to games based on beefsacks list or in collection
```

# What is this? {-}

This notebook contains a set of analyses for predicting upcoming board games for prominent reviewers and users in the world of boardgaming. 

Using data on games and user collections from boardgamegeek, I trained models at the individual user level to predict how likely a user is to add an upcoming game to their collection. This analysis is not focused on predicting how a reviewer will *rate* a game, but simply whether they will add it to their collection.

To see an example of training a user specific model, click on the following link: https://phenrickson.github.io/bgg_reports/user_reports/mrbananagrabber_2020.html. This notebook illustrates the process of training a model to predict my own collection.

Last Updated: `r Sys.Date()`

# The Data

I currently am running this analysis for reviewers from Shut Up and Sit Down (Quinns and Ava), Zee Garcia (The Dice Tower) Rahdo, So Very Wrong About Games (Mark Bigney and Mike Walker), Just Three Minute Board Games, WatchItPlayed Board Game Barrage (right now, only Christina). I also analyze Rodney Smith from WatchItPlayed, who doesn't so much as review games as make incredibly helpful tutorials, but I still refer to the entire group as 'reviewers' from here on out. 

```{r summarize collections by reviewer}

# count games by outcome
summarized = games_and_collections_data %>%
        select(username, date, games_and_collection) %>%
        unnest(games_and_collection) %>%
        mutate_at(vars(c("prevowned","own", "owned", "rated")),
                  ~ case_when(. == 'yes' | . == 1 ~ 1,
                              TRUE ~ 0)) %>%
        mutate(owned_not_rated= case_when(rated == 0 & owned == 1 ~ 1,
                                          TRUE ~ 0)) %>%
        mutate(played = case_when(own == 1 | rated == 1 | prevowned == 1 ~ 1,
                                  TRUE ~ 0)) %>%
        select(username, date, game_id, name, own, owned, rated, prevowned, owned_not_rated, played) %>%
        group_by(username, date) %>%
        summarize(`Currently Own` = sum(own),
                  `Ever Owned` = sum(owned),
                  `Rated, Own, or Previously Owned` = sum(played),
                  `Previously Owned` = sum(prevowned),
                  Rated = sum(rated),
                  `Owned But Not Rated` = sum(owned_not_rated),
                  .groups = 'drop') %>%
        gather("variable", "value",
               -username, -date) %>%
        mutate(shame = case_when(variable == 'Own But Not Rated' ~ 'yes',
                                 TRUE ~ 'no')) %>%
        mutate(variable = factor(variable,
                                 levels = c("Rated",
                                            "Currently Own",
                                            "Previously Owned",
                                            "Ever Owned",
                                            "Owned But Not Rated",
                                            "Rated, Own, or Previously Owned"))) %>%
        mutate(max = max(value)) 
```

There are a number of different outcomes on boardgamegeek for every reviewer's collection. The outcome I am interested in modeling is 'Ever Owned' - has a user ever added game to their collection?

```{r table of game outcomes by reviewer}

summarized %>%
        select(username, variable, value) %>%
        spread(variable, value) %>%
        arrange(desc(`Rated, Own, or Previously Owned`)) %>%
        flextable() %>%
        autofit() %>%
        bg(., j = 'Ever Owned',
           bg = 'grey80')

```

Some reviewers have owned more games than others, which will make their baseline probability of owning an upcoming game higher than others.

```{r table of games outcome by reviwer plot}

library(forcats)

summarized %>%
        ggplot(., aes(y=reorder_within(username, value, variable),
                      fill = username,
                      label = value,
                      x= value)) +
        geom_col()+
        geom_text(hjust = -0.1, size = 3)+
        scale_y_reordered()+
        facet_wrap(variable ~., ncol =2, scales = "free_y")+
        theme_phil()+
        ylab("username")+
        coord_cartesian(xlim = c(0, summarized$max[1]*1.1))+
        guides(fill = "none")+
        scale_fill_username+
        #cale_fill_colorblind()+
        xlab("number of games")+
        ggtitle("Reviewer Collections by BGG Status")+
        #   subtitle = str_wrap("Number of games by status on BGG for each reviewer")) +
        my_caption


```

I model each user's collection as a function of selected game features, using information about the game on BGG such as mechanics, player count, playing time, category, as well as features for prominent designers, publishers, and artists. The model does not look at outcomes on BGG, such as the number of user ratings or community rating, though I do include the BGG complexity rating (averageweight) as a feature. For predicting upcoming games for reviewers, I first estimate their complexity using a separate model, then use the model's estimated complexity in the reviewer models. The table below shows the set of features being examined by the model.

```{r show features, warning=F, message=F}

user_owned_workflows[4,] %>%
        mutate(fit = map(.workflow, 
                     ~ .x %>% extract_fit_parsnip)) %>%
        pluck("fit", 1) %$%
        fit %$% 
        beta %>% 
        rownames() %>%
        as_tibble() %>%
        mutate(feature = value,
               type = case_when(grepl("artist_", feature) ~ "artist",
                                grepl("averageweight", feature) ~ "bgg outcome",
                                grepl("publisher_", feature) ~ "publisher",
                                grepl("designer_", feature) ~ "designer",
                                grepl("family|category", feature) ~ "bgg category",
                                grepl("mechanic", feature) ~ "mechanic",
                                TRUE ~ "info")) %>%
        mutate(tidied_feature = tidy_name_func(feature)) %>%
        select(feature, tidied_feature, type) %>%
        DT::datatable()

```

# Models

I trained classification models (specifically, penalized logistic regression models) for each individual reviewer using games published before 2021. The outcome is binary, indicating yes when an individual reviewer owned a game and no when they have not.

For each reviewer, the model looks at features of games (mechanics, playing time, category) and how they relate to a user's decision to own a game. If a user has owned a lot of Science Fiction Games, the model will likely find a positive effect for Science Fiction.

```{r get user models, warning=F, include=F}

user_models = user_owned_workflows %>%
        mutate(fit = map(.workflow, 
                          ~ .x %>% extract_fit_parsnip)) %>%
        mutate(tidied = map(fit,
                            ~ .x %>% tidy()))

```

## An Example

To illustrate, here are the top 20 coefficients from **rahdo's** model (after centering and scaling the features to be on the same scale). Features with positive coefficients increase the probability that rahdo will own a game; features with negative coefficients decrease the probability. 

```{r show rahdos model as an example}

user_models %>%
        filter(username == 'rahdo') %>%
        select(username, outcome, tidied) %>%
        unnest(tidied) %>%
        filter(term != '(Intercept)') %>%
        group_by(username, outcome) %>%
        mutate(term = tidy_name_func(term)) %>%
        slice_max(order_by = abs(estimate),
                  n=20) %>%
        ggplot(., aes(x=estimate,
                      color = estimate,
                      y = reorder_within(term, estimate, username)))+
        facet_wrap(username ~.,
                   ncol = 3, 
                   scales = "free_y")+
        geom_point()+
        theme_phil()+
        theme(legend.title = element_text(size=8))+
        geom_vline(xintercept =0,
                   linetype = 'dotted')+
        scale_y_reordered()+
        ylab("feature")+
        xlab("effect on owning game (log-odds)")+
        scale_color_gradient2(low = "red",
                              mid = "grey60",
                              high = "deepskyblue2",
                              limits = c(-0.1, 0.1),
                              oob = scales::squish)+
        guides(color = guide_colorbar(barwidth = 15,
                                      barheight = 0.5,
                                      title = "Decreases Probability                               Increases Probability",
                                      title.position = 'top',
                                      label = F))+
        theme(strip.text.x = element_text(size = 14))

```

This means that Rahdo is more likely to own a game if it's been published recently (an increase in the year the game was published), if it has more mechanics and a higher minimum age, and if it has set collection or has been published by Rio Grande. 

Conversely, Rahdo is less likely to own wargames, games with a higher minimum player count, childrens games, or games with take that mechanics.

If you've watched a lot of rahdo, as a I have, this probably makes sense. He is always running through new games and frequently adds ones he likes to his collection, and he tends to like somewhat complex economic/worker placement games. He dislikes wargames and take that mechanics, and since he mostly plays games at two players he's less likely to own a game if it has a higher minimum player count.

## Individual Reviewer Models

A 'model' for an individual user is an equation that relates how features of a game affect the probability that a user will own it. The values, or coefficients, in that equation are learned by looking at the user's historical data. 

The following plot displays the top 25 coefficients from each reviewer's model.

```{r check on models, warning=F, message=F, fig.height=12, fig.width=10}

user_models %>%
        select(username, outcome, tidied) %>%
        unnest(tidied) %>%
        filter(term != '(Intercept)') %>%
        group_by(username, outcome) %>%
        mutate(term = tidy_name_func(term)) %>%
        slice_max(order_by = abs(estimate),
                  n=25) %>%
        ggplot(., aes(x=estimate,
                      color = estimate,
                      y = reorder_within(term, estimate, username)))+
        facet_wrap(username ~.,
                   ncol = 3, 
                   scales = "free_y")+
        geom_point()+
        theme_phil()+
        theme(legend.title = element_text(size=8))+
        geom_vline(xintercept =0,
                   linetype = 'dotted')+
        scale_y_reordered()+
        ylab("feature")+
        xlab("effect on owning game (log-odds)")+
        scale_color_gradient2(low = "red",
                              mid = "grey60",
                              high = "deepskyblue2",
                              limits = c(-0.1, 0.1),
                              oob = scales::squish)+
        guides(color = guide_colorbar(barwidth = 15,
                                      barheight = 0.5,
                                      title = "Decreases Probability                               Increases Probability",
                                      title.position = 'top',
                                      label = F))+
        ggtitle(paste("What predicts a user's collection?", sep=""),
                subtitle = str_wrap(paste("Top coefficients from a penalized logistic regression for games owned by specified user. Predictors centered and scaled. Model trained on games published prior to", 2021), 120))+
                theme(strip.text.x = element_text(size = 12))


```

To put it more simply, here are the top 5 positive/negative features for each reviewer, which we can think of as their likes/dislikes.

```{r get likes and dislikes for each reviewer, warning=F}

user_models %>%
        select(username, outcome, tidied) %>%
        unnest(tidied) %>%
        filter(term != '(Intercept)') %>%
        group_by(username, outcome) %>%
        mutate(term = tidy_name_func(term)) %>%
        slice_max(order_by = estimate,
                  n=5) %>%
        mutate(type = 'likes') %>%
        bind_rows(.,
                  user_models %>%
                          select(username, outcome, tidied) %>%
                          unnest(tidied) %>%
                          filter(term != '(Intercept)') %>%
                          filter(username != 'mrbananagrabber' & username != 'Phil') %>%
                          group_by(username, outcome) %>%
                          mutate(term = tidy_name_func(term)) %>%
                          slice_min(order_by = estimate,
                                    n=5) %>%
                          mutate(type = 'dislikes')
                  ) %>%
        ungroup() %>%
        select(username, term, type) %>%
        arrange(username) %>%
        pivot_wider(id_cols = c("username"),
                    values_from = c("term"),
                    names_from = c("type")) %>%
        # mutate(likes = map(likes, ~ paste(paste("\U2191", .x), collapse="\n")),
        #        dislikes = map(dislikes, ~ paste(paste("\U2191", .x), collapse="\n"))) %>%
        mutate(likes = map(likes, ~ paste(.x, collapse="\n")),
               dislikes = map(dislikes, ~ paste(.x, collapse="\n"))) %>%
        unnest(likes, dislikes) %>%
        flextable() %>%
        autofit() %>%
        color(., j = 'likes',
              part = 'all',
           color = 'deepskyblue2') %>%
        color(., j= 'dislikes',
              part = 'all',
           color = 'red')
        
```


# Predicting Upcoming Games

I trained each reviewer's model on games published before 2021. I now use these models to predict games published from 2021 and onwards for each reviewer.

A couple of notes here. Since I'm using the averageweight of the game on BGG as a feature, which is itself an outcome voted on by BGG users that we won't necessarily know for newly released games, I first use a separate model to estimate the complexity of upcoming games. I then use the estimated averageweight in my models.

I additionally flag some games as having potentially incorrect or misleading data. If a game has more than 15 mechanics while having a low complexity, it's likely the data is incorrect.

```{r load averageweight bgg outcomes model and recipe, include=F}

# # load recipe
# bgg_outcomes_recipe = readr::read_rds(here::here("models", "active", "base_recipe.Rdata"))

# # load workflow
# bgg_outcomes_final_workflows = readr::read_rds(here::here("models", "active", "bgg_outcomes_final_workflows.Rds"))

# load just the complexity model
bgg_complexity_workflow = readr::read_rds(here::here("models", "active", "bgg_complexity_workflow.Rds"))

```


```{r get upcoming games and estimate complexity, warning=F, message=F, results = 'hide', include =F}

# load model for estimating averageweight
# get list of games to predict
games_upcoming = games_model %>%
        filter(yearpublished >= 2021) %>%
        mutate(own = NA,
               owned = NA,
               rated = NA,
               rating = NA,
               dataset = 'upcoming') %>%
        mutate(log_usersrated = log1p(usersrated)) %>%
        filter(!is.na(yearpublished)) %>%
        filter(usersrated > 5) 
  #      filter(bayesaverage > 0)

# estimate complexity
games_upcoming_estimated_averageweight = bgg_complexity_workflow %>%
        predict(new_data = games_upcoming) %>%
        bind_cols(., games_upcoming %>%
                          select(game_id)) %>%
        rename(averageweight = .pred) %>%
        left_join(., games_upcoming %>%
                          select(-averageweight),
                  by = "game_id")

```

```{r now predict upcoming games with user models, include=F}

# predict for each user
games_upcoming_probs = user_owned_workflows %>%
        mutate(preds = map(.workflow,
                           ~ .x %>% 
                                   predict(games_upcoming_estimated_averageweight, type = 'prob') %>%
                                   bind_cols(., games_upcoming_estimated_averageweight %>%
                                                     select(game_id, name, yearpublished)))) %>%
        select(username, outcome, preds) %>%
        unnest(preds) %>%
        left_join(., user_collections_tidied,
                  by = c("game_id", "username")) %>%
        mutate(owned = case_when(own == 1 | prevowned == 1 ~ 'yes',
                                 TRUE ~ 'no')) %>%
        mutate(rated = case_when(!is.na(rating) ~ 'yes',
                                 TRUE ~ 'no')) %>%
        mutate(own = case_when(own == 1 ~ 'yes',
                               TRUE ~ 'no')) %>% 
        mutate_at(vars(c("preordered", 
                         "prevowned",
                         "want")),
                  ~ case_when(. == 1 ~ 'yes',
                              TRUE ~ 'no')) %>%
        select(username, outcome, .pred_no, .pred_yes, game_id, name, yearpublished, own, owned, rated, preordered, want)

```

```{r warning flags}

upcoming_flags = games_upcoming_estimated_averageweight %>%
        select(game_id, name, averageweight, starts_with("mechanic")) %>%
        mutate(number_mechanics = rowSums(select(., starts_with("mechanic")))) %>%
        filter(number_mechanics > 15 & averageweight < 3) %>%
        select(name, game_id)

flag_games_func = # get col funcs
        scales::col_factor(
                palette = "grey90",
                na.color = NA,
                ordered=F,
                levels = upcoming_flags$name)

```

```{r create function for tidying up reviewers}

# tidy
reviewers_tidied = gsub("%20", "", reviewers)

# make function for displaying in flextables
display_name_func = function(x) {
        
        x %>%
                gsub("%20", "", .) %>%
                abbreviate(., minlength=8) %>%
                str_pad(., width=8, side = "both")
               
}

# make df with versions of names
reviewers_df = data.frame("username" = reviewers,
                          "username_tidied" = gsub("%20", "", reviewers),
                          "username_abbr" = display_name_func(reviewers))
               

```

## Highest Probability Games

What upcoming games are most likely to be owned by these reviewers? I simply take the mean of reviewer probabilities for each game and sort, looking at games that have the highest probability across all reviewers. The following table shows probabilities for every reviewer and can be filtered and sorted for any reviewer. For any game, click on its name to go straight to its profile on BGG.

```{r make datatable for reviewer probs}

prob_table = games_upcoming_probs %>%
        select(yearpublished, game_id, name, .pred_yes, username) %>%
        left_join(., reviewers_df %>%
                          mutate(username = username_tidied),
                  by = c("username")) %>%
        select(-username, -username_tidied) %>%
        rename(username = username_abbr) %>%
     #   filter(!(game_id %in% upcoming_flags$game_id)) %>%
                group_by(username) %>%
                arrange(desc(.pred_yes)) %>%
           #     mutate(rank = row_number()) %>%
      #          select(-.pred_yes) %>%
     #   spread(username, rank) %>%
                spread(username, .pred_yes) %>%
        mutate(Mean = rowMeans(select(., all_of(reviewers_df$username_abbr)))) %>%
               # mutate(Mean = round(Mean, 2)) %>%
        select(yearpublished, game_id, name, Mean, everything()) %>%
                mutate_if(is.numeric, round, 2) %>%
                mutate_at(vars(reviewers_df$username_abbr),
                ~ case_when(. == 1 ~ .99,
                            . == 0 ~ .01,
                            TRUE ~ .)) %>%
        arrange(desc(Mean)) %>%
              #  arrange(Mean) %>%
        mutate_at(vars(c("yearpublished",
                         "game_id", 
                         "name")),
                       ~ as.character(.)) %>%
        mutate(yearpublished = factor(yearpublished)) %>%
        rename(Published = yearpublished,
               ID = game_id,
               Name = name) %>%
        mutate(Name = paste('<a href="https://boardgamegeek.com/boardgame/', ID, '">', Name, '</a>', sep="")) %>%
        select(-ID)


# make breaks
breaks<-quantile(seq(.01, .99, .01), probs = seq(.01, .99, .05))

#  breaks = weight_deciles
colorRamp=colorRampPalette(c("white", "deepskyblue1"))
col_palette <- colorRamp(length(breaks)+1)

# display table
prob_table %>%
        datatable(escape=F,
                  filter = 'top',
                  options = list(pageLength = 25,
                                 scrollX=F,
                                 autowidth=T,
                                 columnDefs = list(list(className = 'dt-center', targets = which(names(prob_table)!='Name')-1))),
                             #    columnDefs=list(list(width = '30px', targets = c(which(names(prob_table)!='Name')-1)))),
                                                # list(width = '400px', targets = c(which(names(prob_table)=='Name')-1)))),
                                       #  targets = seq(3, ncol(prob_table)-1))),
                  rownames = F) %>%
        formatStyle(names(prob_table %>% select(-Published, -Name)), backgroundColor = styleInterval(breaks, col_palette))
```

<!-- The following table displays top 100 games in a table - click on the ID or Name to go straight to the boardgamegeek profile for a given game. -->

```{r make flextable func}

make_reviewer_flextable_func = function(input_data, n=50) {
        
        input_data %>%
          select(yearpublished, game_id, name, .pred_yes, username) %>%
        left_join(., reviewers_df %>%
                          mutate(username = username_tidied),
                  by = c("username")) %>%
        select(-username, -username_tidied) %>%
        rename(username = username_abbr) %>%
        filter(!(game_id %in% upcoming_flags$game_id)) %>%
                group_by(username) %>%
                arrange(desc(.pred_yes)) %>%
           #     mutate(rank = row_number()) %>%
      #          select(-.pred_yes) %>%
     #   spread(username, rank) %>%
                spread(username, .pred_yes) %>%
        mutate(Mean = rowMeans(select(., all_of(reviewers_df$username_abbr)))) %>%
               # mutate(Mean = round(Mean, 2)) %>%
        select(yearpublished, game_id, name, Mean, everything()) %>%
                mutate_if(is.numeric, round, 2) %>%
                mutate_at(vars(reviewers_df$username_abbr),
                ~ case_when(. == 1 ~ .99,
                            . == 0 ~ .01,
                            TRUE ~ .)) %>%
        arrange(desc(Mean)) %>%
              #  arrange(Mean) %>%
        mutate_at(vars(c("yearpublished",
                         "game_id", 
                         "name")),
                       ~ as.character(.)) %>%
        rename(Published = yearpublished,
               ID = game_id,
               Name = name) %>%
        mutate(Link = paste("https://boardgamegeek.com/boardgame/", ID, sep="")) %>%
        mutate(Rank = row_number()) %>%
        head(50) %>%
        flextable(col_keys = c("Rank", "Published", "ID", "Name", "Mean", reviewers_df$username_abbr)) %>%
        compose(j= 3,
                value = as_paragraph(
                        hyperlink_text(x = ID,
                                       url = Link)
                )) %>%
        compose(j= 4,
                value = as_paragraph(
                        hyperlink_text(x = Name,
                                       url = Link)
                )) %>%
        bg(.,
           bg = col_func,
           j = c("Mean",
                 reviewers_df$username_abbr)) %>%
        bg(., 
           bg = 'grey90',
           i = ~  ID %in% as.character(upcoming_flags$game_id)
           ) %>%
        # set_formatter(.,
        #               Mean = function(x) sprintf( "%.1f%%", x*100),
        #               Gyges = function(x) sprintf( "%.1f%%", x*100),
        #               Quinns = function(x) sprintf( "%.1f%%", x*100),
        #               rahdo = function(x) sprintf( "%.1f%%", x*100),
        #               WatchItPlayed = function(x) sprintf( "%.1f%%", x*100),
        #               ZeeGarcia = function(x) sprintf( "%.1f%%", x*100)) %>%
        autofit() %>%
        flextable::color(j = c("Name",
                               "ID"),
                         color ="skyblue4") %>%
        bold(., j = c("Name", "ID"),
             part = 'body') %>%
        flextable::align(part = c("all"),
                         align = 'center',
                         j = c("Mean",
                               reviewers_df$username_abbr)) %>%
        autofit()
        
                             }

```


<!-- ```{r all games, warning=F, message=F} -->

<!-- make_reviewer_flextable_func(games_upcoming_probs, n=100) -->

<!-- ``` -->

## Comparing Reviewer Predictions

How do reviewer predictions compare? I'll look at the correlation (Spearman) between the probabilities for each reviewer.

```{r compare correlation}

games_upcoming_probs %>%
        select(yearpublished, game_id, name, .pred_yes, username) %>%
        filter(!(game_id %in% upcoming_flags$game_id)) %>%
        spread(username, .pred_yes) %>%
        select(all_of(reviewers_tidied)) %>%
        cor(method = 'spearman') %>%
        ggcorrplot(hc.order = TRUE, 
                   lab = T,
                 #  type = 'lower',
                   outline.color = "white")+
        theme(axis.text.x= element_text(size = 8,
                                       angle = 45))+
        theme(axis.text.y = element_text(size = 8))

```

Ava (AlabasterCrippens) is most correlated with Quinns and aboardgamebarrage, while Mark Bigney (Gyges) is most correlated with Just Three Minute Board Games (J_3MBG) and Walker (VWValker). The least correlated reviewers are Zee and Mark Bigney, who evidently have very different preferences for games: for instance, Mark rates Tigris & Euphrates at 9.5 (his highest rating) while Zee rates it a 4.


<!-- ```{r show walker and mark bigneys probabilities, fig.height=8} -->

<!-- games_upcoming_probs %>% -->
<!--         select(yearpublished, game_id, name, .pred_yes, username) %>% -->
<!--         # group_by(username) %>% -->
<!--         # arrange(desc(.pred_yes)) %>% -->
<!--         # mutate(rank = row_number()) %>% -->
<!--         # pivot_wider(id_cols = c("name"), -->
<!--         #             values_from = c(".pred_yes", "rank"), -->
<!--         #             names_from = c("username")) %>% -->
<!--         # unnest() -->
<!--         spread(username, .pred_yes) %>% -->
<!--         select(name, Gyges, VWValker) %>% -->
<!--         ggplot(., aes(x=Gyges,  -->
<!--                       y=VWValker,  -->
<!--                       label = name))+ -->
<!--         geom_point(alpha = 0.5)+ -->
<!--         geom_text(check_overlap = T, -->
<!--                   vjust = -1)+ -->
<!--         theme_phil()+ -->
<!--         my_caption+ -->
<!--         stat_cor(method = 'spearman') -->

<!-- ``` -->

# Top Games by Year

In this section I make heat tables of predicted probabilities for specific years.

## Top Games 2021

```{r top games 2021}

make_reviewer_flextable_func(games_upcoming_probs %>%
                                     filter(yearpublished==2021))

```

## Top Games 2022

```{r top games 2022}

make_reviewer_flextable_func(games_upcoming_probs %>%
                                     filter(yearpublished==2022))

```

## Top Games 2023

```{r top games 2023}

make_reviewer_flextable_func(games_upcoming_probs %>%
                                     filter(yearpublished==2023))

```

# Top Games by Reviewer

In this section I look at the top games for individual reviewers by year. I rank each reviewer's top games according to their model, then highlight in blue games that the reviewer has already added to their collection.

```{r try to make flextable differently, warning=F, message=F}

input_years = c(2021, 2022, 2023)

get_fts = 
        foreach(i = 1:length(input_years)) %do% {
                
                input_set_year = input_years[i]
                
                games_owned = games_and_collections_data %>%
                        select(username, games_and_collection) %>%
                        unnest(games_and_collection) %>%
                        select(username, yearpublished, game_id, name, owned) %>%
                        gather("variable", "value",
                               -username, -yearpublished, -game_id, -name) %>%
                        filter(value == 'yes') %>%
                                filter(yearpublished == input_set_year)
                
                # create table by year
                user_table = games_upcoming_probs %>%
                        filter(!(game_id %in% upcoming_flags$game_id)) %>%
                        filter(yearpublished == input_set_year) %>%
                        group_by(username) %>%
                        slice_max(., order_by = .pred_yes, n=25, with_ties = F) %>%
                        select(username, yearpublished, name) %>%
                        pivot_wider(., id_cols = "yearpublished",
                              names_from = c("username"),
                              values_from = c("name")) %>%
                          unnest()
                
                # get column names
                user_names = names(user_table[,-1])
                
                # display table with colors
                ft = user_table %>%
                        mutate(Published = as.character(yearpublished)) %>%
                        select(-yearpublished) %>%
                        mutate(Rank = row_number()) %>%
                        select(Rank, Published, everything()) %>%
                        flextable(col_keys = c("Rank", "Published", reviewers_tidied)) %>%
                        bg(., 
                           bg = flag_games_func,
                           j = user_names) %>%
                           bg(., j = 'Gyges',
                           i = ~ Gyges %in% (games_owned %>%
                                                     filter(username == 'Gyges') %>%
                                                     pull(name)),
                           bg = 'deepskyblue1') %>%
                        bg(., j = 'ZeeGarcia',
                           i = ~ ZeeGarcia %in% (games_owned %>%
                                                     filter(username == 'ZeeGarcia') %>%
                                                     pull(name)),
                           bg = 'deepskyblue1') %>%
                        bg(., j = 'Quinns',
                           i = ~ Quinns %in% (games_owned %>%
                                                     filter(username == 'Quinns') %>%
                                                     pull(name)),
                           bg = 'deepskyblue1') %>%
                        bg(., j = 'rahdo',
                           i = ~ rahdo %in% (games_owned %>%
                                                     filter(username == 'rahdo') %>%
                                                     pull(name)),
                           bg = 'deepskyblue1') %>%
                        bg(., j = 'WatchItPlayed',
                           i = ~ WatchItPlayed %in% (games_owned %>%
                                                     filter(username == 'WatchItPlayed') %>%
                                                     pull(name)),
                           bg = 'deepskyblue1') %>%
                        bg(., j = 'J_3MBG',
                           i = ~ J_3MBG %in% (games_owned %>%
                                                     filter(username == 'J_3MBG') %>%
                                                     pull(name)),
                           bg = 'deepskyblue1') %>%
                        bg(., j = 'VWValker',
                           i = ~ VWValker %in% (games_owned %>%
                                                     filter(username == 'VWValker') %>%
                                                     pull(name)),
                           bg = 'deepskyblue1') %>%
                        bg(., j = 'AlabasterCrippens',
                           i = ~ AlabasterCrippens %in% (games_owned %>%
                                                     filter(username == 'AlabasterCrippens') %>%
                                                     pull(name)),
                           bg = 'deepskyblue1') %>%
                        flextable::align(part = c("header"),
                                         align = 'center',
                                         j =  reviewers_df$username_tidied) %>%
                        flextable::set_header_labels(., values =
                                                             split(reviewers_df$username_abbr, reviewers_df$username_tidied)) %>%
                        flextable::color(color = 'grey20', part='all') %>%
                        autofit()
        
                ft
        }


```

## Top Games by Reviewer 2021

```{r show reviewer top picks for 2021, warning=F, message=F}

pluck(get_fts, 1)

```

## Top Games by Reviewer 2022

```{r show reviewer top picks for 2022, warning=F, message=F}

pluck(get_fts, 2)

```

## Top Games by Reviewer 2023

```{r show reviewer top picks for 2023, warning=F, message=F}

pluck(get_fts, 3)

```


```{r save predictions to local, warning=F, message=F, include=F}

# save this to a location
readr::write_rds(games_upcoming_probs %>%
                         mutate(date = Sys.Date()) %>%
                         select(date, everything()),
                 file = here::here("predictions", paste("reviewer_probs_", Sys.Date(), ".Rdata", sep="")))

```

