---
title: "Examining BGG Categories"
author: Phil Henrickson
params:
        train_year: 2020
        min_ratings: 50
---

```{r setup, include=F, results = 'hide', message=F, warning=F}

source(here::here("src", "helpers", "exploratory_setup.R"))

```

```{r load functions for categorical, include=F} 

source(here::here("src", "functions", "categorical_functions.R"))

```


```{r create tidy games, include=F}

# set minimum ratings
min_ratings = params$min_ratings

# train year
train_year = params$train_year

# remove unreleased and problem games
tidy_games =
        analysis_games %>%
        # remove unreleased and problem games
        filter(!(game_id %in% c(
                unreleased_games$game_id,
                drop_games$game_id))
        ) %>%
        # filter out games with missingness on yearpublished
        filter(!is.na(yearpublished)) %>%
        # filter out games with missingness on average weight
        filter(!is.na(averageweight) & averageweight!=0) %>%
        # filter our kickstarter editions and big box editions
        #  filter(!(grepl("kickstarter|big box|mega box|megabox", tolower(name)))) %>%
        # filter to games released prior to current year
        filter(yearpublished < year(Sys.Date())) %>%
        # filter to games with at least X votes
        filter(usersrated >= min_ratings) %>%
        # set yearpublished to numeric
        mutate(yearpublished = as.numeric(yearpublished))

```

```{r functions and captions}

# caption
my_caption = 
        list(labs(caption = paste(paste("data from boardgamegeek.com as of", max(as.Date(tidy_games$load_ts))),
                                  #    paste("analysis by phil henrickson"),
                                  paste("phenrickson.github.io/data-analysis-paralysis/boardgames.html"), sep="\n")))

```

This notebook provides some basic exploratory analysis of games on boardgamegeek (BGG) in support of my work [predicting ratings for upcoming games] and [predicting games for individual users]. 

For this write up, I examine games published through `r train_year` that have achieved at least `r min_ratings` user ratings by the time of writing.[^ I have additionally excluded some games that were cancelled or never released, or have data quality issues with their profiles on BGG.]

What are the categories of games on BGG and how do they relate to community ratings?

# Categories

## Top Categories by BGG Outcome

What are the most frequent categories on BGG? How are games within each category typically rated? 

```{r most common categories, warning=F, message=F}

p = game_categories %>%
        group_by(type, id, value) %>%
        summarize(games = n_distinct(game_id),
                  .groups = 'drop') %>%
        slice_max(games, n = 50, with_ties=F) %>%
        arrange(desc(games)) %>%
        mutate(rank = row_number()) %>%
        mutate(page = case_when(rank %in% seq(1, 25) ~ "1-25",
                                rank %in% seq(26, 50) ~ "26-50")) %>%
        mutate(value = abbreviate(value, minlength=25)) %>%
        ggplot(aes(y=reorder(value,games),
                   x=games,
                   text = paste(
                           paste("category:", reorder(value, games)),
                           paste("games:", games),
                           sep = "\n")))+
        geom_col()+
        theme_phil()+
        theme(axis.text.y = element_text(size = 8),
              strip.text.x = element_text(size = 6))+
        facet_wrap(. ~ page,
                   scales = "free_y")+
        scale_x_continuous(breaks = scales::pretty_breaks(n=3))+
        ylab("Category")+
        xlab("Number of Games")

plotly::ggplotly(p,
                 tooltip = 'text')
        
```

I'll then plot the distribution of games with the 25 most frequent categories. What types of categories are typically associated with heavier games? What category is the highest rated (on average)?

```{r plot categories}

plot_games_by_categorical(game_categories,
                          25)

```

Finally, the following (interactive) table displays the mean of each BGG outcome by category. Use the filters below the column names to filter through the table by category or number of games. 

```{r make summary table}

# summarize data
summary_data = game_categories %>%
        summarize_games_by_categorical()


# color gradients
colorRampDiv = colorRampPalette(c("red", "white", "lightskyblue1"))
blueRampSeq = colorRampPalette(c("white", "skyblue1"))
redRampSeq = colorRampPalette(c("white", "orange"))

# generate table
summary_data %>%
        make_categorical_summary_table()

```

## Combinations of Categories

What are the most frequent pairings of categories in games on BGG? The following visualization displays an upset plot of the most frequent combinations of categories used in games.

```{r upset plot}

upset = game_categories %>%
        filter(game_id %in% tidy_games$game_id) %>%
        select(type, value, game_id) %>%
        mutate(has_type = 1) %>%
        pivot_wider(names_from = value, 
                    values_from = has_type,
                    values_fill = list(has_type = 0)) %>%
        as.data.frame() %>%
        UpSetR::upset(nsets = 15,
                      nintersects = 30,
                      keep.order = T,
                      order.by = c("freq"),
                      mb.ratio = c(0.4, 0.6))

```

The bar chart on the bottom left indicates the number of games in each category. The bar chart on the top indicates the number of games with a **combination** of categories. That is, the most common category in games has typically been Card-Games, and there are many games in which Card Game is their only category. The most frequent combination of categories, historically, has been Fantasy + Card Game and Science Fiction + Wargame.

```{r print upset, out.width='100%'}

print(suppressMessages({
        upset
}))

```


