---
title: "Examining BGG Mechanics"
author: Phil Henrickson
params:
        train_year: 2020
        min_ratings: 50
---

```{r setup, inclue=F, results = 'hide', message=F, warning=F}

source(here::here("src", "helpers", "exploratory_setup.R"))

```

```{r load functions for categorical, include=F} 

source(here::here("src", "functions", "explore_categorical_functions.R"))

```


```{r create tidy games, include=F}

# set minimum ratings
min_ratings = params$min_ratings

# train year
train_year = params$train_year

# remove unreleased and problem games
tidy_games =
        analysis_games %>%
        # remove unreleased and problem games
        filter(!(game_id %in% c(
                unreleased_games$game_id,
                drop_games$game_id))
        ) %>%
        # filter out games with missingness on yearpublished
        filter(!is.na(yearpublished)) %>%
        # filter out games with missingness on average weight
        filter(!is.na(averageweight) & averageweight!=0) %>%
        # filter our kickstarter editions and big box editions
        filter(!(grepl("kickstarter|big box|mega box|megabox", name))) %>%
        # filter to games released prior to current year
        filter(yearpublished < year(Sys.Date())) %>%
        # filter to games with at least X votes
        filter(usersrated >= min_ratings) %>%
        # set yearpublished to numeric
        mutate(yearpublished = as.numeric(yearpublished))

```

```{r functions and captions}

source(here::here("src", "functions", "explore_categorical_functions.R"))

# caption
my_caption = 
        list(labs(caption = paste(paste("data from boardgamegeek.com as of", max(as.Date(tidy_games$load_ts))),
                                  #    paste("analysis by phil henrickson"),
                                  paste("phenrickson.github.io/data-analysis-paralysis/boardgames.html"), sep="\n")))

```

This notebook provides some basic exploratory analysis of games on boardgamegeek (BGG) in support of my work [predicting ratings for upcoming games] and [predicting games for individual users]. 

For this write up, I examine games published through `r train_year` that have achieved at least `r min_ratings` user ratings by the time of writing.[^ I have additionally excluded some games that were cancelled or never released, or have data quality issues with their profiles on BGG.]

What kinds of mechanics are there on BGG and how do they relate to community ratings?

# Mechanics

## Top Mechanics by BGG Outcome

What are the most frequent mechanics on BGG? How are games with each mechanic typically rated? 

```{r most common mechanics, warning=F, message=F}

game_mechanics %>%
        group_by(type, id, value) %>%
        summarize(games = n_distinct(game_id),
                  .groups = 'drop') %>%
        slice_max(games, n = 50, with_ties=F) %>%
        arrange(desc(games)) %>%
        mutate(rank = row_number()) %>%
        mutate(page = case_when(rank %in% seq(1, 25) ~ "1-25",
                                rank %in% seq(26, 50) ~ "26-50")) %>%
        mutate(value = abbreviate(value, minlength=25)) %>%
        ggplot(aes(y=reorder(value,games),
                   x=games))+
        geom_col()+
        theme_phil()+
        theme(axis.text.y = element_text(size = 8),
              strip.text.x = element_text(size = 6))+
        facet_wrap(. ~ page,
                   scales = "free_y")+
        scale_x_continuous(breaks = scales::pretty_breaks(n=3))+
        ylab("Mechanic")+
        xlab("Number of Games")
        

```

I'll then plot the distribution of games with the 25 most frequent mechanics. What types of mechanics are typically associated with heavier games? What mechanic is the highest rated (on average)?

```{r plot mechanics}

plot_games_by_categorical(game_mechanics,
                             25)

```

Finally, the following interactive table displays the mean of each BGG outcome by mechanic. 

```{r make summary table}

# summarize data
summary_data = game_mechanics %>%
        summarize_games_by_categorical()


# color gradients
colorRampDiv = colorRampPalette(c("red", "white", "lightskyblue1"))
blueRampSeq = colorRampPalette(c("white", "skyblue1"))
redRampSeq = colorRampPalette(c("white", "orange"))

# generate table
summary_data %>%
        make_categorical_summary_table()

```

## Combinations of Mechanics
 
What are the most frequent pairings of mechanics in games on BGG? The following visualization displays an upset plot of the most frequent combinations of mechanics used in games.

```{r upset plot}

upset = game_mechanics %>%
        filter(game_id %in% tidy_games$game_id) %>%
        select(type, value, game_id) %>%
        mutate(has_type = 1) %>%
        pivot_wider(names_from = value, 
                    values_from = has_type,
                    values_fill = list(has_type = 0)) %>%
        as.data.frame() %>%
        UpSetR::upset(nsets = 15,
                      keep.order = T,
                      order.by = c("freq"),
                      mb.ratio = c(0.6, 0.4))

```

The bar chart on the bottom left indicates the number of games with a specific mechanic. The bar chart on the top indicates the number of games with a **combination** of mechanics. That is, the most common mechanic in games is Dice-Rolling, and there are many games in which Dice-Rolling is the only mechanic. The most frequent combination of mechanics is Simulation + Hexagon Grid + Dice-Rolling.

```{r print upset, fig.height = 8}

print(suppressMessages({
        upset
}))

```


